---
title: "p8105_hw1_kw3180"
author: Kino Watanabe
data: 2025-09-18
output: github_document
---

# Problem 1

```{r}
library(moderndive)
library(tidyverse)
```

## Importing and looking at data set
```{r}
data("early_january_weather")
```

There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The variables in the dataset are: origin, year, month, day, hour, temp (range: 24.08, 57.92), dewp (range: 8.96, 53.06), humid (range: 32.06, 100), wind_dir (range: 0, 360), wind_speed (range: 0, 24.16638), wind_gust (range: 16.11092, 31.07106), precip (range: 0, 0.19), pressure (range: 1010.8, 1034.4), visib (range: 0.12, 10), and time_hour (range: 2013-01-01 01:00:00, 2013-01-15 23:00:00). The mean is `r mean(pull(early_january_weather, temp))`.

## Scatterplot

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point() +
    labs(
    title = "Temperature vs. Time",
    x = "Time (hourly)",
    y = "Temperature",
    color = "Humidity"
  )

ggsave("scatter_plot.pdf", height = 4, width = 6)
```

The temperature fluctuated throughout the day, but there is an upward trend in general through the month. As time passed in January, the temperature increased. The humidity seemed to increase throughout the month as well.

# Problem 2

## Create a dataframe
```{r}
set.seed(1234)

p2_df = tibble(
  norm_samp = rnorm(10),
  vec_char = letters[1:10],
  vec_logical = rnorm(10) > 0,
  factor_vec = factor(rep(c("level1","level2","level3"), length.out = 10),
        levels = c("level1","level2","level3"))
)

p2_df
```
## Creating means
```{r}
mean(pull(p2_df, norm_samp))
mean(pull(p2_df, vec_char))
mean(pull(p2_df, vec_logical))
mean(pull(p2_df, factor_vec))
```

We can find the mean of the random sample of size 10 from a standard normal distribution (mean =  `r mean(pull(p2_df, norm_samp))`) and a logical vector indicating whether elements of the sample are greater than 0 (mean = `r mean(pull(p2_df, vec_logical))`). We can't find the mean for a character vector of length 10 and a factor vector of length 10, with 3 different factor “levels."

## Using as.numeric
```{r, results = 'hide', warning=FALSE}
as.numeric(pull(p2_df, norm_samp))
as.numeric(pull(p2_df, vec_char))
as.numeric(pull(p2_df, vec_logical))
as.numeric(pull(p2_df, factor_vec))
```

We can find the mean of the random sample of size 10 from a standard normal distribution because this is a numeric variable. As shown with as.numeric, this just gave us our 10 numbers of our random sample. We can find the mean of the a logical vector indicating whether elements of the sample are greater than 0 because R converted "True" and "False" as binary "1" and "0," respectively. Converting the logical vector into a binary number enabled us to find the mean, although nonsensical. 

We couldn't find the mean for a character vector of length 10 because it is a character variable. When we try to convert it as a numeric variable with as.numeric, R cannot process it and returns "NA."

When we try to find the mean for a factor vector of length 10, with 3 different factor “levels,” we cannot do it because it is a ordinal categorical variable. When we convert it into numeric with as.numeric, it codes the levels as integer codes for levels. Even if we took the mean for these factors, it would be meaningless because the numbers are arbitrary labels.

